Containers and R---the Rockerverse and beyond

### 2019-12-13 manuscript.Rmd
enterprise software section - one sentence per line, add reference

At T-Mobile, R is used to power real-time services that are called over a million times a day. T-Mobile created a set of neural network machine learning natural language processing models to help customer care agents manage text-based messages for customers. The models are convolutional neural networks that use the RStudio Keras package and are built on top of a Rocker Docker image. Since the models power tools for agents and customers, they need to have extremely high uptime and reliability--and they found that R is able to perform. The AI @ T-Mobile team open sourced [their docker images](https://github.com/tmobile/r-tensorflow-api  which are available on GitHub.

>>>>

At T-Mobile, R is used to power real-time services that are called over a million times a day.
T-Mobile created a set of neural network machine learning natural language processing models to help customer care agents manage text-based messages for customers \citep{t-mobile_enterprise_2018}.
The models are convolutional neural networks that use the RStudio Keras package and are built on top of a Rocker Docker image.
Since the models power tools for agents and customers, they need to have extremely high uptime and reliability--and they found that R is able to perform.
The AI @ T-Mobile team open sourced their Docker images [on GitHub](https://github.com/tmobile/r-tensorflow-api).
